---
title: "Get to know me!"
author: "Caleb Ji"
date: "2026-01-27"
output:
  html_document:
    toc: true                   # this is to generate a table of contents
    toc_depth: 2                # this is to control what level of header we are going to display on the table of contents 
    toc_float: true             #this is to have a floating table of contents
    code_folding: hide          # this is to fold/hide the code 
bibliography: references.bib    # this is for the citations/bibliography 
link-citations: true            # this is for the citations/bibliography 
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE, # suppressing warning messages
                      message = FALSE,
                      knitr.kable.max_rows = 6)

# attach any relevant packages
library(kableExtra)
library(dplyr)

# read the data files
courses <- read.csv(file = "courses.csv")
hobbies <- read.csv(file = "hobbies.csv")
```

# This R Markdown is to get to know Caleb Ji!

## Bio {#bachelors-degree}
Hi, My name is Caleb! I'm a fourth year student in UofT.


## Bachelors Degree 
### {#bachelors-degree-table}
**Table 1. Record of all undergraduate courses** 
``` {r courses_table, include=TRUE,echo=TRUE}

# show a table with all my courses 
# ... fill in ...
courses %>%
  kbl() %>%
  kable_styling()

```

### {#bachelors-degree-figure}

``` {r courses_figure, include=TRUE,echo=TRUE, fig.cap = "**Figure 1 Title** Text "}
## organize the data for plotting
# ... fill in ...



# generate plot 
# ... fill in ...
  
```

## Hobbies
### {#my-hobbies}
I have hobbies!

## Custom section {#custom-section}
I am cool!

## Questions to answer 

1.[ What is your bachelors degree?](#bachelors-degree)

2.[Which courses have you taken and in which departments?](#bachelors-degree-figure)

3.[What are your hobbies?](#my-hobbies)

4.[How many hours a week do you spend on each hobby?](#hobbies-hours-per-week)

5.[What is your favorite hobby?](#favorite-hobby)

6.[Add a custom section of your choosing!](#custom-section)

## Citations
... fill in ...
